The challenge and promise of software citation for credit, identification, discovery, and reuse

### 2016-04-07 SC-challenge.tex
a few minor edits to table

Develop infrastructure to support indexing of software citations along with (or complementary to) the existing publication citation ecosystem &
The FORCE11 software citation implementation working group will also work on this, in collaboration with publishers and indexers \\

@@

Increase cultural acceptance of the concept of software as a digital product &
Acceptance will happen over time; unclear how to accelerate \\
\bottomrule
\end{tabular}}
\end{table}

>>>>

Develop infrastructure to support indexing of software citations along with (or complementary to) the existing publication citation ecosystem &
The FORCE11 Software Citation Implementation Working Group will also work on this, in collaboration with publishers and indexers \\

@@

Increase cultural acceptance of the concept of software as a digital product &
Acceptance will happen over time; unclear how to accelerate this process \\
\bottomrule
\end{tabular}}
\end{table}
